Fractional Types

### 2019-11-22 fracGC/p.tex
minor typo

As the diagram below (take from Abramsky's
paper~\cite{dblp:conf/calco/abramsky05}) illustrates, this is not a
trivial construction in the sense that the permutation from $A$ to $B$
uses $C$ in non-trivial ways.

>>>>

As the diagram below (taken from Abramsky's
paper~\cite{dblp:conf/calco/abramsky05}) illustrates, this is not a
trivial construction in the sense that the permutation from $A$ to $B$
uses $C$ in non-trivial ways.
